\documentclass[12pt]{report}
\usepackage{color}

\begin{document}

\title{Problem Statement for OpenBazaar} 
\author{Team 3 - Fair Traders \\ Connor Sheehan - sheehacg \\Danny Mandel - mandeldr \\ Shandelle Murray - murras25}
\date{\today}
	
\maketitle

Humans have traded goods and services between each other for mutual gain since the creation of the marketplace. In the past, two individuals who wished to trade would interact directly and resolve their issues through a trusted third party acting as a mediator, such as a mutual friend or a notary. This method was efficient and allowed maximum gain for each party involved. 
	
In the modern age, trading is primarily done through the internet. Due to the phenomenon of globalization, two people who have never met, or never will meet, can trade with each other from across the globe. Centralized services such as eBay or Amazon can connect these two people who otherwise would not have connected. This centralized medium of trade is convenient, but comes with a catch; the middle man often asks for a cut of the gains from each party. 

\textcolor{red}{
Unfortunately, there are a few main problems concerning the current selection of online marketplaces. First of all, as mentioned above, it is not optimal to sacrifice a portion of the profits from online sales to third party corporations. This is an issue that is inevitable in centralized marketplaces. Secondly, many peer to peer networks are not able to serve millions of traders worldwide as it would make use of too many resources technologically to connect so many people. A relatively efficient style of peer to peer network would need to be implemented to accomplish this task. Finally, maintaining fairness of trade without the use of a third party corporation is inherently more challenging and another method of mediation would have to be considered. It is highly important that a useful method of resolving common disputes, such as incorrect product shipped, damaged goods, or a buyer who refuses payment, be implemented.}

\textcolor{red}{People looking to buy, sell, and trade over the internet are the main stakeholders of an endeavour to develop an ideal avenue for online trade.} In order to benefit from trade as much as possible, such people require a decentralized, anonymous method of interaction over the internet. Buyers and sellers should be able to access a free, global market from any desktop computer with an uncensored internet connection. This is particularly applicable to traders in regions with limited free trade or excessive government intervention as they especially require an uncensored, anonymous method to access these markets. \textcolor{red}{It is important that traders are able to interact with one another without sacrificing profits to a third party and without sacrificing fairness.}
	
Overall, providing a free, open market accessible to everyone that utilizes a universal currency will revolutionize the online marketplace. This will allow sellers and online businesses to flourish, effectively reducing the overhead costs of trade and preventing large corporations from directly profiting from transactions. The marketplace will then be able to return to its previous fairness and simplicity, now on a global scale.


\end{document}










