\documentclass[12pt]{report}

\usepackage{xcolor} % for different colour comments

%% Comments
\newif\ifcomments\commentsfalse

\ifcomments
\newcommand{\authornote}[3]{\textcolor{#1}{[#3 ---#2]}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\else
\newcommand{\authornote}[3]{}
\newcommand{\todo}[1]{}
\fi

\newcommand{\wss}[1]{\authornote{magenta}{SS}{#1}}
\newcommand{\hm}[1]{\authornote{blue}{HM}{#1}} %Hediyeh
\newcommand{\tz}[1]{\authornote{blue}{TZ}{#1}} %Tahereh
\newcommand{\pl}[1]{\authornote{blue}{PL}{#1}} %Peng

\begin{document}

\title{Problem Statement for OpenBazaar} 
\author{Team 3 - Fair Traders \\ Connor Sheehan - sheehacg \\Danny Mandel - mandeldr \\ Shandelle Murray - murras25}
\date{\today}
	
\maketitle

Humans have traded goods and services between each other for mutual gain since the creation of the marketplace. In the past, two individuals who wished to trade would interact directly and resolve their issues through a trusted third party acting as a mediator, such as a mutual friend or a notary. This method was efficient and allowed maximum gain for each party involved. 
	
In the modern age, trading is done through the internet. Due to the phenomenon of globalization, two people who have never met, or never will meet, can trade with each other from across the globe. Centralized services such as eBay or Amazon can connect these two people who otherwise would not have connected. This centralized medium of trade is convenient, but comes with a catch; the middle man often asks for a cut of the gains from each party. 

Vendors and other traders require a decentralized, anonymous method of interaction over the internet. Buyers and sellers should be able to access free, global markets from any desktop computer with an uncensored internet connection. This is particularly applicable to traders in regions with limited free trade or excessive government intervention as they especially require an unce miktelansored, anonymous method to access these markets. Traders must be able to interact with one another without sacrificing profits to a third party; however, this should not be at the expense of guaranteeing fairness. Use of an unbiased mediator that does not directly benefit from the transaction would provide a useful method of resolving common disputes, such as incorrect product shipped, damaged goods or a buyer who refuses payment.
	
Overall, providing a free, open market accessible to everyone that utilizes a universal currency will revolutionize the online marketplace. This will allow sellers and online businesses to flourish, effectively reducing the overhead costs of trade and preventing large corporations from directly profiting from transactions. The marketplace will then be able to return to its previous fairness and simplicity, now on a global scale.


\noindent \wss{This is an example comment.  You can turn comments off by replacing
  commentstrue by commentsfalse.}\\
\hm{Sample comment}\\
\tz{Sample comment}\\
\pl{Sample comment}

\end{document}










